---
title: "Data Visualization 2018 Survey"
author: "Mara Averick"
date: '`r Sys.Date()`'
output:
  html_document:
    keep_md: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.retina = 2)
```

Based on [2018 Data Visualizatio Survey Results](https://medium.com/@Elijah_Meeks/2018-data-visualization-survey-results-26a90856476b) by Elijah Meeks, (GitHub repo [here](https://github.com/emeeks/data_visualization_survey)).

```{r}
suppressPackageStartupMessages(library(tidyverse))
```

```{r, include = FALSE}
results_2018 <- read_tsv(file = here::here("data", "cleaned_survey_results_2018.tsv"))

# add id row
results_2018 <- results_2018 %>%
  mutate(respondent_id = as.character(row_number()))
```

```{r}
skimr::skim_to_list(results_2018)
```


```{r, include = FALSE}
write_csv(results_2018, path = here::here("output", "survey_results_2018.csv"))
```

Get only records with responses to "thought leaders" question.[^whom]

```{r}
thought_leaders <- results_2018 %>%
  select(one_of(c("respondent_id", 
                  "Who do you look to as a thought leader in data visualization?"))) %>%
  rename("leader" = "Who do you look to as a thought leader in data visualization?") %>%
  filter(!is.na(leader))

head(thought_leaders)
```

Looks like there's more than one answer per respondent (_duh_)! Let's use `separate_rows()` to tidy things up a bit.

```{r}
thought_leaders <- thought_leaders %>%
  separate_rows(leader, sep = ",") %>%
  mutate(leader = tolower(leader))
```

```{r, include = FALSE}
thought_leaders <- read_csv(here::here("output", "thought_leaders.csv"),
                            col_types = cols(respondent_id = col_character())) %>%
  filter(!is.na(leader)) %>%
  mutate(leader = tolower(leader))
```

```{r}
skimr::skim(thought_leaders)
```

Let's look at the "thought leaders" chosen by more than one respondent (I'm just assuming someone didn't bother to write one name repeatedly, though I guess one could filter for that if so desired).

```{r}
leader_board <- thought_leaders %>%
  count(leader, sort = TRUE) %>%
  filter(n > 1)

head(leader_board, n = 10)
```

Now we can rank them, and get the frequencies of leader mentions as a percentage of the total of leaders mentioned more than one time in the survey.

```{r}
leader_mentions <- leader_board %>%
  mutate(leader = forcats::fct_infreq(leader, ordered = TRUE)) %>%
  summarise(total = sum(n))
  
leader_board <- leader_board %>%
  mutate(total = leader_mentions$total,
         rank = dense_rank(desc(n)),
         freq = n/total)
```

```{r, fig.height = 6, fig.width = 10}
top_10 <- leader_board %>%
  filter(rank <= 10)

top_10 %>%
  mutate(leader = forcats::fct_reorder(leader, as.numeric(n))) %>%
  ggplot(aes(leader, n)) +
  geom_col(colour = "#ffba82", fill = "#ffba82", alpha = 0.9) + 
  scale_y_continuous(expand=c(0,0)) +
  coord_flip() +
  labs(title = "Most mentioned thought leaders", 
       subtitle = "Who do you look to as a thought leader in data visualization?",
       caption = "source: 2018 Data Visualization Survey, https://github.com/emeeks/data_visualization_survey") +
  hrbrthemes::theme_ipsum_rc() +
  theme(plot.background = element_rect(colour = "#f7f6f5"),
        text = element_text(family = "Concourse T4"),
        plot.title = element_text(family = "Concourse T4", face = "bold"),
        plot.subtitle = element_text(family = "Concourse T3"),
        axis.text.x = element_text(family = "Concourse T2"))

```



[^whom]: Yes, it _should_ be "whom," but Elijah is a barbarian, so we'll just have to take things as they are.
